---
title: "Cross Validation"
author: "Amanda Howarth"
date: "11/23/2019"
output: github_document
---

## NOTES
Model selection - what belongs in my model, what does not belong in my model? 
AIC/BIC models are for NON nested models 
if one model is more complex but has similar fit, choose the less complex!
mean squared error = smaller values are better

cross validation will tell u if a model looks better than another in terms of prediction accuracy

Prediction as a goal 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelr)
library(mgcv)
```

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() 
```

## Training and testing 
fit models by hand, see how they work out 

```{r}
train_df = sample_frac(nonlin_df, size = .8)
train_df %>% view 

# anti says gives u everything that does not appear in the other data set (training dataset), the data sets will not overlap at all 
test_df = anti_join(nonlin_df, train_df, by = "id")

#a plot will show the red as the testing data set.. see how ur black points make predictions on the red points

ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

## fit three models of varying goodness. 

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

Lets look at some fits 

```{r}
train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")

train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```
wiggly fit is like keeping all 40 variables in ur model, where smooth fit is only picking the variables that matter, and the underfit is just putting in one variable 

```{r}
train_df %>% 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red") + 
  facet_wrap(~model)
```

CROSS VALIDATION! 
make predictions and compute the root mean square error on that designated set 
(for some data u have never seen before.. as opposed to the lines above that are showing the fit for the data u do see and have)
```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```
on average the squared distance is about 0.62. (lower number is better, better at predicting)

we want to know which model will do better on the testing data set... u generally know which would do better on the training set. training set has more stuff (like phone numbers etc) so test data set is smaller and u are testing it 

## Do this all using modelr

ok so now we prefer to not test things by hand and to also do it many times
use modelr!
cross_vs generates pairs for cross validation 
generates 100 testing pairs in a testing frame
```{r}
cv_df = 
  crossv_mc(nonlin_df, 100) 
```

```{r}
cv_df %>% pull(train) %>% .[[1]] %>% as_tibble
# gives 80 rows, can pull out the data sets by choosing [[2]] or [[3]] etc 

cv_df %>% pull(test) %>% .[[1]] %>% as_tibble

cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

Try fitting the linear model to all of these (to all of the training data sets)
* apply linear models to all datasets 
* data is whatever that training set it (.x)

map 2 gives u two columns 
```{r}
cv_df = 
  cv_df %>% 
  mutate(linear_mod  = map(train, ~lm(y ~ x, data = .x)),
         rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y))
  )


cv_df = 
  cv_df %>% 
  mutate(linear_mod  = map(train, ~lm(y ~ x, data = .x)),
         smooth_mod  = map(train, ~mgcv::gam(y ~ s(x), data = .x)),
         wiggly_mod  = map(train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))) %>% 
  mutate(rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
         rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)),
         rmse_wiggly = map2_dbl(wiggly_mod, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

```{r}
child_growth = read_csv("./data/nepalese_children.csv")

```

```{r}


```




